Analysis paper

### 2021-06-01 analysis/analysis.Rmd
update table width

```{r}
# create helper function to make table
make_score_table <- function(scores, 
                             group = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  table <- scores[,!c("Target")] %>%
    kable(format = "html", col.names = c(" ", names(scores)[-(1:2)])) %>% #format = "markdown"
    collapse_rows(columns = 1) %>%
    kable_styling(bootstrap_options = "striped") %>%
    column_spec(1, background = "white")

@@

@@

    tables[[name]] <- make_score_table(tmp_df, 
                                       group = FALSE) %>%
      pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)

>>>>

```{r}
# create helper function to make table
make_score_table <- function(scores, 
                             group = TRUE, 
                             full_width = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  table <- scores[,!c("Target")] %>%
    kable(format = "html", col.names = c(" ", names(scores)[-(1:2)])) %>% #format = "markdown"
    collapse_rows(columns = 1) %>%
    kable_styling(bootstrap_options = "striped", 
                  full_width = full_width) %>%
    column_spec(1, background = "white")

@@

```{r fig.height=10, fig.width=5}

@@

    tables[[name]] <- make_score_table(tmp_df, 
                                       group = FALSE, 
                                       full_width = FALSE) %>%
      pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
